\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{SmarteRun: Coding The Portable Coach}

### 2014-05-12 final/article.tex
Refine captions in results

 \For{i = 0; i < 5000; i++}{  
Choose a random run $r$ in $S$\\
Choose a random (time,distance) point in $r$ as $(t,d)$\linebreak\linebreak
Calculate the true secant line $l_t$ from $(t,d)$ to the end of the run\\
Slope($l_t$) = true average pace for the rest of the run\linebreak\linebreak
Use the SmarteRun algorithm to model a predicted run using $t$, $d$, and total distance\linebreak\linebreak
Calculate the secant line $l_p$ from $(t,d)$ to the end of the predicted run\\
Slope($l_p$) = predicted average pace for the rest of the run
 }
 Calculate error between each $l_t$ and $l_p$
 \caption{Assessing the accuracy of a run prediction}
\end{algorithm}

@@

Overall the results indicated a RMSE of 2.3088. As can be seen in the figure below, in general average pace was close to predicted pace (as shown by the large cluster of data points along the line $x=y$). However, clear groups of outliers exist, particularly in predicting too fast of a pace. A simple solution to reduce error would be capping the pace that we predict at $10 m/s$ (this pace represents one of the fastest human sprints, and is highly unlikely to be exceeded by recreational runners).

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{longshort.png}
\caption{A graph comparing actual pace with predicted pace with long runs shown in red and short runs in blue. }
\end{center}
\end{figure}

>>>>

 \For{i = 0; i < 5000; i++}{  
Choose a random run $r$ in $S$\\
Choose a random (time,distance) point in $r$ as $(t,d)$\linebreak\linebreak
Calculate the true secant line $l_t$ from $(t,d)$ to the end of the run\\
Slope($l_t$) = true average pace for the rest of the run\linebreak\linebreak
Use the SmarteRun algorithm trained on $S - r$ to model a predicted run using $t$, $d$, and total distance\linebreak\linebreak
Calculate the secant line $l_p$ from $(t,d)$ to the end of the predicted run\\
Slope($l_p$) = predicted average pace for the rest of the run
 }
 Calculate error between each $l_t$ and $l_p$
 \caption{Assessing the accuracy of a run prediction}
\end{algorithm}

@@

We calculated the actual and predicted paces for 5000 random points in our data set. Overall the results indicated a RMSE of 2.3088. As can be seen in the figure below, in general average pace was close to predicted pace (as shown by the large cluster of data points along the line $x=y$). However, clear groups of outliers exist, particularly in predicting too fast of a pace. A simple solution to reduce error would be capping the pace that we predict at $10 m/s$ (this pace represents one of the fastest human sprints, and is highly unlikely to be exceeded by recreational runners).

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=6cm]{longshort.png}
\caption{A graph comparing actual pace with predicted pace. Predictions on long runs are shown in red and short runs in blue. }
\end{center}
\end{figure}
